On exponential sums arising from the classical doubling method

### 2025-04-08 main.tex
Remove algebraic group

We recall that \[
	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
\]
with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \algebraicGroup{\GL}_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.

>>>>

We recall that \[
	\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n} = \prod_{a \in \mathbb{Z}/m\mathbb{Z}} \left(\algebraicGroup{\GL}_n\right)_a
\]
with Frobenius root action $$\Frobenius(g_0,g_1, \hdots, g_{m-1}) = (\Frobenius(g_{m-1}), \Frobenius(g_0), \Frobenius(g_1), \hdots, \Frobenius(g_{m-2})).$$ We will freely identify $\restrictionOfScalars{\finiteFieldExtension{m}}{\finiteField}{\algebraicGroup{\GL}_n}(\finiteField) = \GL_n(\finiteFieldExtension{m})$ via the map $\left(g_0,\dots,g_{m-1}\right) \mapsto g_0$.
